Calculating life expectancy and exploring missingness

### 2017-04-06 Code/1_Explore_Data.Rmd
moved data

for(i in 1:length(included.states)) { 
  name = paste0('dat_clean_', included.states[i], '.csv')
  ds_temp = dat.clean[dat.clean$state == included.states[i], ]
  write.csv(ds_temp, file=name)
}
rm(ds_temp)
```

>>>>

for(i in 1:length(included.states)) { 
  name = paste0('dat_clean_', included.states[i], '.csv')
  ds_temp = dat.clean[dat.clean$state == included.states[i], ]
  write.csv(ds_temp, file = paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Data/", name))
}
rm(ds_temp)
```
